% !TEX program = xelatex
\documentclass{article}


\usepackage[utf8]{inputenc}
\usepackage{titlesec}
\usepackage{titling}
\usepackage[margin=1in]{geometry}
\usepackage[american]{babel}
\usepackage{csquotes, xpatch}
\usepackage{hyperref}
\usepackage{xcolor}
\usepackage{hyperref}
%\usepackage{fancyhdr} % headers and footers
%\usepackage{bookmark} % To suppress "rerunfilecheck Warning:..."
% Define base style for publist (before loading biblatex)
\newcommand*\publistbasestyle{custom-authoryear}
% Use biblatex-publist for publication and presentation lists
\usepackage[bibstyle=publist, backend=biber, plauthorhandling=highlight, defernumbers=true, linktitles=none, doi=false, isbn=false, url=false, hlyear=false, marginyear=true, plnumbering=none, sorting=ddnt, natbib=true, minbibnames=3, maxbibnames=3]{biblatex}



\usepackage{fontspec}
  \setmainfont{Avenir Light}
  %% Set bold font
  %% https://tex.stackexchange.com/questions/25184/set-the-font-weight-lighter-bolder/27402#27402
  %\setmainfont[BoldFont={* Demi Bold}]{Avenir Next}
  %\newfontfamily\semibold{Avenir Next Demi Bold}
  %\newfontfamily\regsemi[BoldFont={* Demi Bold}]{Avenir Next}

% Bibiography formatting
\setlength{\bibitemsep}{.75\baselineskip plus 0.5\baselineskip}
% \setlength{\bibhang}{.5em}
% No letters after years
\AtEveryCitekey{\clearfield{extradate}}
\AtEveryBibitem{\clearfield{extradate}}

% \addbibresource{preprints.bib}
\addbibresource{pubs-conference.bib}
\addbibresource{pubs-journal.bib}
\addbibresource{talks-presented.bib}
\addbibresource{talks-contributed.bib}
\addbibresource{posters-presented.bib}
\addbibresource{posters-contributed.bib}

% Define formatting for publication margin year
\renewcommand*\plmarginyear[1]{
  \flushright{#1}
}

% \renewcommand*\plmarginyear[1]{%
% \raggedleft\textbf{#1}%
% }

% \renewcommand*\plmarginyear[1]{%
% \raggedleft\small\textbf{#1}%
% }

% Specify author name to bold in publication list
\plauthorname[Owen][]{Morgan}
\plauthorname[Owen P.][]{Morgan}
\plauthorname[O][]{Morgan}
\plauthorname[O. P.][]{Morgan}

% Define function for changing margin size (for publist)
\def\changemargin#1#2{\list{}{\rightmargin#2\leftmargin#1}\item[]}
\let\endchangemargin=\endlist

% Define the default entry command - year, content
\newcommand{\entry}[5]{

  \begin{minipage}[t]{.15\textwidth}
    \begin{flushright}
      \hfill {#1}
    \end{flushright}
  \end{minipage}
  \hfill\vline\hfill
  \begin{minipage}[t]{.80\textwidth}
    \textbf{#2}

    \ifx&#3&
      {#3}\textit{#4}
    \else
      {#3, }\textit{#4}

    \fi
    \footnotesize{#5}
  \end{minipage}\\\vspace{.25cm}
}

% Define award entry command - year, title, details
\newcommand{\awardentry}[3]{
  \begin{minipage}[t]{.15\textwidth}
    \begin{flushright}
      \hfill {#1}
    \end{flushright}
  \end{minipage}
  \hfill\vline\hfill
  \begin{minipage}[t]{.80\textwidth}
    \textbf{#2}

    \footnotesize{#3}
  \end{minipage}\\\vspace{.25cm}
}

% Define the skill entry command - title, details
\newcommand{\skillentry}[2]{
  {\hspace{2em}\textbf{#1}:}
  {#2}
  \vspace{.25cm}
}

% No indentation
\setlength{\parindent}{0in}

% Macros
\newcommand{\cu}{Cornell University}
\newcommand{\sjc}{St. John's College}
\newcommand{\jhusom}{Johns Hopkins University School of Medicine}

% Hyperlinks
\let\oldhref\href
\renewcommand{\href}[3][blue]{\oldhref{#2}{\color{#1}{#3}}}


% Section formatting
\titleformat{\section}
{\large\bfseries}
{}
{0em}
{}[\titlerule]

\titleformat{\subsection}
{\center\large\bfseries}
{}
{0em}
{}

\titleformat{\subsubsection}[runin]
{\bfseries}
{\hspace{0em}}
{0em}
{}[:]

\titlespacing{\subsubsection}
{0em}{.25em}{.25em}

\renewcommand{\maketitle}{
  \begin{minipage}[t]{.5\textwidth}
    \begin{flushleft}
      \textit{Last updated \thedate}
    \end{flushleft}
  \end{minipage}
  \begin{minipage}[t]{.5\textwidth}
    \begin{flushright}
      {\huge\bfseries
      \theauthor}

      \vspace{.25em}

      \cu, Department of Psychology

      Experience and Cognition Lab

      opm6@cornell.edu

    \end{flushright}
  \end{minipage}
}

\author{Owen Morgan}
\title{CV}

% Update date set to last compile:
\date{\today}

\begin{document}

\maketitle

\section{Education}

\entry
{2020~\textendash~Now}
{PhD Student, Psychology/Cognitive Science}
{\cu}{Ithaca, New York}
{Committee: Daniel Casasanto (chair), Jesse Goldberg, Felix Thoemmes. Major in Developmental Psychology, Minor in Cognitive Science.}

\entry
{2013~\textendash~2017}
{BA in Liberal Arts}
{\sjc}{Annapolis, Maryland}
{All-required curriculum based on closely reading original sources; equivalent to a double major in Philosophy, and the History of Mathematics and Science.}

\section{Professional Experience}

\entry
{2017~\textendash~2020}
{Research Assistant, Cognitive Neuropsychiatric Research Laboratory}
{\jhusom}{Baltimore, Maryland}
{Studied the cerebellum’s role in cognition and conducted several fMRI projects under the mentorship of Cherie Marvel.}

\entry
{Summers 2016 \newline 2015}
{Research Assistant, Blumenfeld Lab}
{Yale Medical School}{New Haven, Connecticut}
{Studied conscious visual perception under the mentorship of Hal Blumenfeld.}

\section{Publications}

% Change margins for publist's marginal years
% \begin{changemargin}{1in}{0in}

% \subsection{Preprints}
% \newrefsection[preprints]
% \nocite{*}
% \printbibliography[heading=none]

\subsection{Conference Papers}
\newrefsection[pubs-conference]
\nocite{*}
\printbibliography[heading=none]

\subsection{Journal Articles}
\newrefsection[pubs-journal]
\nocite{*}
\printbibliography[heading=none]


% Restore margins
% \end{changemargin}

\section{Presentations}

\subsection{Talks}
\newrefsection[talks-presented]
\nocite{*}
\printbibliography[heading=none]

\subsection{Talks (contributed)}
\newrefsection[talks-contributed]
\nocite{*}
\printbibliography[heading=none]

\subsection{Posters}
\newrefsection[posters-presented]
\nocite{*}
\printbibliography[heading=none]

\subsection{Posters (contributed)}
\newrefsection[posters-contributed]
\nocite{*}
\printbibliography[heading=none]


\section{Honors and Awards}

\awardentry{2023}{Martha E. Foulk and Ethel B. Waring Fellowships}
{Research fellowship providing funding for Fall Semester.}

\awardentry{}{Glushko \& Samuelson Student Travel Grant}
{Funded travel to 45th Conference of the Cognitive Science Society, Sydney.}

\awardentry{}{Cognitive Science @ Cornell Travel Award}
{Funded travel to 45th Conference of the Cognitive Science Society, Sydney.}

\awardentry{}{Cornell Graduate School Travel Grant}
{Funded travel to 45th Conference of the Cognitive Science Society, Sydney.}

\awardentry{}{Cognitive Science @ Cornell Graduate Research Award}
{Funded data collection for a study on frequency asymmetry in vision.}

\awardentry{2022}{Cornell Graduate School Travel Grant}
{Funded travel to 44th Conference of the Cognitive Science Society, Toronto.}

\awardentry{}{Cognitive Science @ Cornell Travel Award}
{Funded travel to 44th Conference of the Cognitive Science Society, Toronto.}

\awardentry{2020}{Travel Award for 9th Ataxia Investigators Meeting (Conference moved online)}
{Awarded to abstracts selected for “hot chair” presentation. Award cancelled; conference moved online due to COVID-19.}

\awardentry{2017}{Pathways Fellowship}
{Funded Neurobiology course at Harvard Extension Summer School.}

\awardentry{2016 \newline 2015}{Hodson Trust Internship Grant}
{Funded summer research on conscious visual perception at Yale University.}

\section{Teaching and Mentorship}

\subsection{Teaching Assistantships}

\entry{Spring 2023}{TA, Human Perception: Applications to Computer Graphics, Art, and Visual Display (COGST 3420)}
{\cu}{Ithaca, New York}
{Instructor: David Field.}

\entry{Fall 2022, 2020}{TA, Human Brain and Mind: Introduction to Cognitive Neuroscience (HD 2200)}
{\cu}{Ithaca, New York}
{Instructor: Daniel Casasanto.}

\entry{Summer 2022}{TA, Introduction to Cognitive Science (COGST 1101)}
{\cu}{Ithaca, New York}
{Instructor: Adam Broitman.}

\entry{Spring 2022}{TA, Gender and Psychopathology (HD 3320)}
{\cu}{Ithaca, New York}
{Instructor: Lauren Korfine.}

\entry{Fall 2021}{TA, Research Methods (HD 2380)}
{\cu}{Ithaca, New York}
{Instructor: Lauren Korfine.}

\entry{Spring 2021}{TA, Adolescence (HD 1170)}
{\cu}{Ithaca, New York}
{Instructor: Robert Sternberg.}

\entry
{2014~\textendash~2017}
{Lab Assistant}
{\sjc}{Annapolis, Maryland}
{Worked with professors to lead class discussions; set up, demonstrated, and explained historical experiments from biology, physics, and chemistry.}

\subsection{Guest Lectures}

\entry{Summer 2022}{Introduction to Cognitive Science (COGST 1101)}
{\cu}{Ithaca, New York}
{"The Cognitive Neuroscience of Consciousness"}

\entry{Fall 2021}{Research Methods (HD 2380)}
{\cu}{Ithaca, New York}
{"Scientific Writing"}

\subsection{Mentorship}

\entry{2021~\textendash~Now}{Research Assistant Supervision (Cornell)}
{\cu}{Ithaca, New York}
{Sanyum Dalal, Benjamin Dever-Mendenhall, Jeffrey Iyamah, Rebecca Karpel, Mahek Majithia, Madelyn \mbox{Minor}, and Kira Pawletko.}

\entry{2018~\textendash~2020}{Research Assistant Supervision (JHU)}
{\jhusom}{Baltimore, Maryland}
{Bronte Wen, Deeya Bhattacharya, and Nikita Gupta.}






\section{Technical Skills}

\skillentry{fMRI}
{Collection and quality assurance (3T, 7T), preprocessing, analysis (SPM)}

\skillentry{Eye-tracking}{Collection, preprocessing, analysis}

\skillentry{Scripting}{R/tidyverse, Python, MATLAB}

\skillentry{Data visualization}{R/ggplot, Inkscape, Illustrator}

\skillentry{Task development}
{Python/PsychoPy, ePrime, Inquisit}

\skillentry{Online data collection}
{Prolific, Qualtrics, Inquisit Web}

\skillentry{Web}{HTML/CSS, JavaScript/TypeScript, Django}

\skillentry{Markup}{\LaTeX, RMarkdown}

\skillentry{OS}{Linux, Windows, MacOS}

\section{Spoken Languages}
\skillentry{English}{Native}

\skillentry{Spanish}{Full professional proficiency (ILR scale)}


\raggedleft
\href{https://github.com/opmorgan/cv}{Source code for this CV}

\end{document}

